HO unification from object language to meta language

### 2024-03-28 paper/main.tex
tex: end example

After unification of the two terms, $X$ is assigned to $\lambda x.\lambda y.x$.
This assignment makes $l_2$ to progress since the \lhs is materialized and by
unification, between $X$ and $\lambda x.Y_{x}$, $Y_x$ is instantiate to $\lambda
y.x$. Once $Y_x$ is instantiated, $l_1$ can progress, and set $H_{xy}$ to $x$.
After all these progresses, $l_1$ and $l_2$ are remove from \linkStore and the
\elpiIn{progress} fixpoint terminates. Next, the second unification problem is
run, and $Z$ is set to $f\appsep(\lambda x.x)$. This unification wakes up $l_3$
and since $Z$ starts with the \elpiIn{app} node, the $\eta$-expanded version of
$Z$ is unified with $\lambda x.f \appsep G_{x}~x$ and $G_x$ is set to $x$.
As last step, we can note that $G$

>>>>

After unification of the two terms, $X$ is assigned to $\lambda x.\lambda y.x$.
This assignment makes $l_2$ to progress since the \lhs is materialized and by
unification, between $X$ and $\lambda x.Y_{x}$, $Y_x$ is instantiate to $\lambda
y.x$. Once $Y_x$ is instantiated, $l_1$ can progress, and set $H_{xy}$ to $x$.
After all these progresses, $l_1$ and $l_2$ are remove from \linkStore and the
\elpiIn{progress} fixpoint terminates. Next, the second unification problem is
run, and $Z$ is set to $f\appsep(\lambda x.x)$. This unification wakes up $l_3$
and since $Z$ starts with the \elpiIn{app} node, the $\eta$-expanded version of
$Z$ is unified with $\lambda x.f \appsep G_{x}~x$ and $G_x$ is set to $x$.
As last step, the last link is progressed and the final \Ho substitution is
$\{X _{} \mapsto \lambda x.\lambda y.x, Y _{x} \mapsto \lambda y.x, 
G _{yx} \mapsto y, Z _{} \mapsto f~\lambda x.x, 
H _{x} \mapsto \lambda y.y\}$.

The decompilation phase is only charged, in this example to solve the mappings,
since no suspended links remain. The only mapping in the list is
\mapping{F}{H}{2}, which will assign the $F$ variable in \Fo{} to $\lambda xy.y$
